\begingroup 
\renewcommand{\section}[2]{\anonsection{Список использованных источников}}
\begin{thebibliography}{00}

\bibitem{lib-sidorenko}
    Васильева Р., Земнухова Л., Сидоренко А. и др.
    Сканирование горизонтов: роль информационных технологий в будущем гражданского общества /
    изд. <<Когито-Центрс>>, Москва 2020.

\bibitem{lib-maximov}
    Максимов В.
    Трансформация цвета при изменении освещения /
    изд. <<Наука>>, Москва 1984.

\bibitem{lib-bayer}
    Bayer B.
    Color imaging array /
    изд. <<US Patent>>, 1975.

\bibitem{lib-borwn}
    Brown M.
    A Software Platform for Manipulating the Camera Imaging Pipeline //
    ECCV, 2016.

\bibitem{lib-demosaic}
    Losson O., Macaire L., Yang Y. and al.
    Comparison of color demosaicing methods //
    HAL, 2010.

\bibitem{lib-gray-world}
    Gray World Assumptions
    [Электронный ресурс] //
    MIT
    URL: http://alumni.media.mit.edu/~wad/color/exp1/newgray/
    (дата обращения: 01.05.2023).

\bibitem{lib-brown-cst}
    Brown M.
    Understanding color and your camera //
    London Imaging Meeting, 2020.

\bibitem{lib-cie}
    Susstrunk S., Buckley R., Swen S.
    Standard RGB color spaces //
    Color and Imaging Conference, 1999.

\bibitem{lib-denoising}
    Antoni B., Bartomeu C., Jean-Michel M.
    A review of image denoising algorithms, with a new one /
    HAL, 2099.

\bibitem{lib-spatial-filters}
    Spatial Filters
    [Электронный ресурс] //
    geeksforgeeks
    URL: https://www.geeksforgeeks.org/spatial-filters-averaging-filter-and-median-filter-in-image-processing/
    (дата обращения: 01.05.2023).

\bibitem{lib-gaussian-filter}
    Gaussian Filter
    [Электронный ресурс] //
    geeksforgeeks
    URL: https://www.geeksforgeeks.org/gaussian-filter-generation-c/
    (дата обращения: 01.05.2023).

\bibitem{lib-nlm}
    Non-local Means Denoising
    [Электронный ресурс] //
    OpenCV
    URL: https://docs.opencv.org/3.4/d5/d69/tutorial\_py\_non\_local\_means.html
    (дата обращения: 01.05.2023).

\bibitem{lib-bilateral}
    Bilateral Filter
    [Электронный ресурс] //
    OpenCV
    URL: https://docs.opencv.org/3.4/d4/d13/tutorial\_py\_filtering.html
    (дата обращения: 01.05.2023).

\bibitem{lib-bm3d}
    Dabov K., Foi A., Katkovnik V. and al.
    Image denoising by sparse 3D transform-domain collaborative filtering //
    IEEE Transactions on Image Processing, 2007.

\bibitem{lib-u-net}
    Ronneberger O., Fischer P., Brox T.
    U-Net: Convolutional Networks for Biomedical Image Segmentation //
    MICCAI, 2015.

\bibitem{lib-deep-isp}
    Schwartz, Eli, Raja.
    Deepisp: Toward learning an end-to-end image processing pipeline //
    IEEE Transactions on Image Processing, 2018.

\bibitem{lib-zurich-raw-rgb}
    Ignatov A., Timofte R. and al.
    Aim 2019 challenge on raw to rgb mapping: Methods and results //
    IEEE/CVF International Conference on Computer Vision Workshop (ICCVW), 2019.

\bibitem{lib-mobile-aim-2020}
    Ignatov A., Timofte R. and al.
    AIM 2020 challenge on learned image signal processing pipeline //
    European Conference on Computer Vision, 2020.

\bibitem{lib-aw-net}
    Linhui D., Xiaohong L. and al.
    Awnet: Attentive wavelet network for image isp //
    European Conference on Computer Vision, 2020.

\bibitem{lib-py-net}
    Ignatov A., Luc G., Timofte R.
    Replacing Mobile Camera ISP with a Single Deep Learning Mode //
    European Conference on Computer Vision, 2020.

\bibitem{lib-aim21}
    Ignatov A., Kuo H., Timofte R. and al.
    Learned Smartphone ISP on Mobile NPUs with Deep Learning, Mobile AI 2021 Challenge: Report //
    IEEE/CVF International Conference on Computer Vision Workshop (ICCVW), 2021.

\bibitem{lib-reverse-gradient}
    Ganin Y, Ustinova E., Ajakan H., Germain P., Larochelle H., Laviolette F., Marchand M., Lempitsky V.
    Domain-adversarial training of neural networks //
    Journal of Machine Learning Research, 2016.

\bibitem{lib-exp-fusion}
    Mertens T., Kautz J., Frank R.
    Exposure fusion: A simple and practical alternative to high dynamic range photography //
    Computer graphics forum, 2009.

\bibitem{lib-vgg-loss}
    Simonyan K., Zisserman A. 
    Very deep convolutional networks for large-scale image recognition //
    arXiv, 2014.

\bibitem{lib-msssim}
    Wang Z., Simoncelli E., Bovik A. 
    Multiscale structural similarity for image quality assessment //
    The Thrity-Seventh Asilomar Conference on Signals, Systems \& Computers, 2003. 

\bibitem{lib-aim-dense}
    Truong P., Danelljan M., Gool L., Timofte R.
    Learning accurate dense correspondences and when to trust them //
    Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition, 2021.

\end{thebibliography}
\endgroup

\clearpage